---
title: "Data 413: Classwork/Lab 1"
author: "Frankie Tyndall"
date: '2022-06-28'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
```

## In three or four sentences, explain why constructing a Function in order to execute tasks, is beneficial or advantageous

   Constructing a function in order to execute tasks is beneficial/advantageous
   because it helps you to decrease the amount of input or computational errors
   that you would have in your code due to repetitive calculations. 
   Functions help you to reuse your code for different inputs, 
   which helps you to properly organize and simplify your code making 
   it easier to follow. Finally, functions allows you to solve complex
   problems to simpler code. 
   
# Write a function (using r code and structure demonstrated in class) to calculate a z score for a given observed value, a mean, and a standard deviation value. And then use your function to find a z score for the following problem. 

Observed value = 25.77,  mean =  23.54,  standard deviation = 2.442

```{r}
z_score <- function(ob, mean, sd){
  (ob - mean)/sd
}

print(paste("The z score is", z_score(25.77, 23.54, 2.442)))
```

## Write a function (using r code and the structure demonstrated in class) to calculate the natural log of a number multiplied by the common log of the same number divided by the cube root of a given prime number.Use your function to find the answer if the number to be used for both log expressions is 32 and the given prime number is 11.

## Also use R code to round your answer to the nearest tenth


```{r}
natural_Common <- function(num, prime){
  V = ((log(num)*log10(num))/(prime^(1/3)))
  return(round(V, digits = 1))
}

natural_Common(32, 11)
```

#Use and show R coding to calculate the standard deviation for each variable of the data table mtcars using the “Special For Loop Method” demonstrated in the class notes

```{r}
mtcars

sd_mtcars <- vector("double", ncol(mtcars))  # 1. output
 for (i in seq_along(mtcars)) {            # 2. sequence
   sd_mtcars[[i]] <- sd(mtcars[[i]])      # 3. body
 }

sd_mtcars
```
