---
title: 'Data 413: Classwork/Lab 3'
author: "Frankie Tyndall"
date: '2022-07-05'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## The three lists 

```{r}

x <- list(2, 4, 5, 9, 1)
y <- list(8, 7, 2, 8, 3)
z <- list(1, 8, 5, 4, 2)

```

## For the lists given above, show and use R code (a map function) to 
## iteratively find the square of the sums across the vectors

```{r}
pmap_dbl(list(x,y,z), sum)^2

```
## The Tibble

```{r}
tribble( ~Student,  ~Gender,    ~Salary,
                   "John",   "Male",       65000,
                   "Alice",  "Female",    73000,
                    "Juan",   "Male",       66000,
                    "Beth",  "Female",    71500,
                    "Denise", "Female",  82000
) -> table
 table
```
## Using the data table above, use and show R code that will output a statement that is descriptive for all rows of the data table.

```{r}
table %>%
  pmap_chr(~ str_glue("{..1} who is {..2}, has a salary of {..3} dollars per year"))
```
## Write a nested loop that will produce a 5 by 5 matrix that whose matrix elements are sums of the corresponding columns and rows.

```{r}
matrix_kk <- matrix( nrow = 5, ncol = 5)
for (m in 1:5) {
  for (n in 1:5) {
    matrix_kk[m, n]<- (m + n)
  }
}
print(matrix_kk)

```
## Use for loop coding to produce the number sequence shown below: Note that the numbers 5 and 10 are missing

```{r}
x <- 1:20
for (val in x){
  if (val == 5)
    next
  if (val == 10)
    next
  print(val)
}

```
