---
title: 'Stat 415 Regression: Classwork/Lab 3'
author: "Frankie Tyndall"
date: '2022-07-07'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(dplyr)
```

## Study of Selling Price of a Home

Study looks at the amount of taxes applied to specific 
selling prices of a home.

x = Taxes

y = selling prices

```{r}
Selling_home <- tribble(~X,  ~Y,
          3104,                 279900,
          1173,                 146500,
          3076,                 237700,
          1608,                 200000,
          1454,                 159900,
          2997,                 499900,
          4054,                 265500,
          3002,                 289900
  ) 


Selling_home
```
## Hypothesis for F-Test

H0:β1=0 # null hypothesis: linear relationship does not exist
HA:β1≠0 # alternative hypothesis: linear relationship does exist


## Use and show R code to produce a scatter plot for the bivariate data.Indicate if your scatter plot shows an outlier.


```{r}
qplot(x = X, y = Y, data = Selling_home, geom = "point")

```
The scatterplot shows that there are one or more outliers present in the bivaridate data. Outliers negatively impact normality, but
the scatterplot does suggest a positive linear relationship.

## Use and show R code to produce a linear model for the bivariate data in the table.

```{r}
lm(Y~X, data = Selling_home)


```
slope = 62.32 
y intercept =  100456.77
y(hat) = 100456.77 + 62.32X

## Use and show R code to produce all of the residuals for your model.

```{r}
model8 <- lm(Y~X, data = Selling_home)
residual_model <- resid(model8)
residual_model



```
## Use and show R code to produce a residual plot for the data. Does your residual plot also suggest the existence of an outlier?

```{r}
model8 <- lm(Y~X, data = Selling_home)
residual_model <- resid(model8)
residual_model

plot(fitted(model8), residual_model)
```
The residual plot does suggest the existence of an outlier in the data. There
are residuals that stand out from the basic pattern of residuals. 

##  Execute an F test in order to determine if a linear model is appropriate.  Use the steps and procedure illustrated in class by making use of an ANOVA table ,the F value, and the F critical number. And of course, indicate if the null hypothesis should be rejected.

```{r}
# 8-2 = 6 degrees of freedom 
model8 <- lm(Y~X, data = Selling_home)
anova(model8)

qf(p=.05, df1=1, df2=6, lower.tail=FALSE)

```
The F value is 2.9181
The the F critical number is 5.987378

Since the F value (2.9181) is less than the F critical number 5.987378, we fail to reject the null hypothesis that B1 = 0. This means that a linear relationship does not exist between X (Taxes) and  Y(Selling Price).

## Which of the two residual plots shown above suggests that a linear model for the associated bivariate data is not appropriate?  Provide a brief comment of justification for your answer.

The residual plot of B suggests that a linear model for the associated bivariate data is not appropriate because the plot is patterned and curved which are not 
indicators of a linear model.
