---
title: 'Data 413: Classwork/Lab 4'
author: "Frankie Tyndall"
date: '2022-07-07'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(dplyr)
library(tidyverse)
```

## Using the web address https://en.wikipedia.org/wiki/ITF_Rankings and the R coding structure presented in class to web scrape the following table found on the page.


```{r}
wikiurl <- read_html(
  "https://en.wikipedia.org/wiki/ITF_Rankings")
ITF_Rankings <- wikiurl%>%
  html_table(., fill = T)

ITF_Rankings[[3]] -> ITF
ITF
```

## Using the web address  https://www.mlb.com/stats/2018 and the R coding structure presented in class, web scrape the table found on the page.


```{r}

wikiurl <- read_html("https://www.mlb.com/stats/2018")
baseballdata2018 <- wikiurl%>%
  html_table(., fill = T)

baseballdata2018[[1]] -> BD2018
BD2018

```
##  Use and show R code to find the average number of hits for all players in the table from number 4

```{r}

hit <- BD2018 %>%
  select(HH)

mean(hit$HH)
```
## Use and show R code to produce a boxplot for the number of hits (use tidyverse/ggplot coding). Use the data table from number 4.

```{r}
boxplot(hit$HH)
```
## Use and show dplyr coding to determine which player had the greatest number of strikeouts using the data table from number 4.

```{r}
strikeout <- BD2018 %>%
  select(c(PLAYERPLAYER, SOSO)) %>%
  arrange(desc(SOSO))

strikeout

```

## Use and show dplyr coding to show the batting averages for Washington Nationals players and Colorado Rockies players using the data table from number4 
```{r}
batting_average <- BD2018 %>%
  filter(TEAMTEAM == "WSH"|TEAMTEAM == "COL") %>%
  select(c(TEAMTEAM, AVGAVG)) %>%
  group_by(TEAMTEAM)
  

batting_average
```
