---
title: 'Data 413: Homework (Web Scraping)'
author: "Frankie Tyndall"
date: '2022-07-08'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(dplyr)
library(tidyverse)
```

## Run the following link that will direct you to a table on the internet. Using 4 or 5 sentences, discuss the content of the table.

The table above has a sample size of 235 countries and dependencies with 12
variables that looks at specific aspects of each country or dependency.
The variables from range from population which looks at the number of people that
reside in each country or dependency to the change is population and the land
area of each. The density, amount of migrants, and fertility rate of each
of the 235 countries/dependencies can also be found in the table. The fertility
rate is average amount of children born (alive) to women of a country over
their lifetime. The last three variables of the data set is the average age in 
each country/dependency, as well as, the urban population percentage, and world 
share. 

## Using the R coding structure that was illustrated in class, transfer the table observed on the internet into R Studio.The table will be imported in tibble form.

```{r}
x <- read_html("https://www.worldometers.info/world-population/population-by-country/")
world_pop <- x %>%
  html_table(., fill = T)

world_pop[[1]] -> world_population 

world_population
```
## Now use R coding and dplyr functions to modify your table, until you get the exact final representation shown below

```{r}
country_namechange <- world_population
names(country_namechange)[2]<-paste("Country")
names(country_namechange)[3]<-paste("Population")

select_country_pop <- country_namechange %>% 
  select(c(Country, Population))

select_country_pop$Population <-
  as.numeric(gsub(",","",select_country_pop$Population))

select_country_pop

country_population <- select_country_pop %>% 
  filter(Country == "China"|Country == "United States"|Country == "Russia"
         |Country == "Vietnam"|Country == "South Africa") %>%
  group_by(Country) %>%
  arrange(desc(Population))

country_population

```
