---
title: 'Stat 415 Regression: Classwork/Lab 8'
author: "Frankie Tyndall"
date: '2022-07-22'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Head Circumference Dataset 

```{r}
tribble(~HEIGHT,          ~WEIGHT,            ~HEADCIRCUMFERENCE,         
        30,                  339,                   47,             
     26.25,                  267,                   42,              
        25,                  289,                   43,              
        27,                  332,                 44.5,              
      27.5,                  272,                   44,              
      24.5,                  214,                 40.5,              
     27.75,                  311,                   44,             
        25,                  259,                 41.5,
        28,                  298,                   46,              
     27.25,                  288,                   44,
        26,                  277,                   44,                   
     27.25,                  292,                 44.5,
        27,                  302,                 42.5,
     28.25,                  336,                 44.5
     ) -> Head_circum
Head_circum
```
## Use and show R code to construct a coefficient matrix. Is there multicollinearity involving any of the explanatory variables?  If so, what variables are of concern? (Head Circumference is the response variable)

```{r}
cor(Head_circum)
```
The predictor variables, height and weight both have high correlations with the
dependent/response variable of Height circumference. There is multicollinearity
between the predictor variables Height and Weight. The correlation coefficient
between the two variables is 0.7847652, this indicates that both of
the variables may not be needed in the model. The predicting power of
the model is not improved if there is high correlation between the height and 
weight variables.

## Use and show R code to produce the full multi regression model where the response variable is Head Circumference and the two explanatory variables are Height and Weight.

```{r}
ml_headcir <- lm(HEADCIRCUMFERENCE~HEIGHT + WEIGHT, Head_circum)
ml_headcir

```
The full regression model:

Head Circumference = 18.82425 + 0.78634*HEIGHT + 0.01281*WEIGHT

## Use and show R code to produce the summary table for your full model.  Indicate the variable whose p value is not significant at the level of .05.  And also indicate what proportion of the variability in Head Circumference is explained by your model.

```{r}

summary(ml_headcir)

```
The weight variable has a p value that is larger than 0.05, specifically it has
a p value of 0.29290, this makes the explanatory variable weight not 
significant. Using the adjusted r-squared value of 0.743, this means that
The model explains 74.3% of the variation in the dependent variable Head Circumference using only those predictor variables that have an impact on the
response variable.

## Use and show R code that will produce a linear regression model with the explanatory variable of no significance removed.

```{r}
removed_variable <- lm(HEADCIRCUMFERENCE~HEIGHT, Head_circum)
removed_variable

summary(removed_variable)
```
Linear Regression Model:

y-hat = 16.382 + 1.016*Height

## Interpret the slope of this model

```{r}
removed_variable
```
The slope indicates that for every increase by 1 inch in height,
a child's head circumference (in centimeters) was found to have increased by
1.016 on average.

## What proportion of the variability of the response variable is not explained by the linear regression model? 

1 -  0.7584 = 0.2416 or 24.16%

24.16% of the variability of the response variable Head Circumference is not
explained by the linear regression model.

## Find the correlation coefficient r  for the linear model


```{r}
cor(Head_circum$HEADCIRCUMFERENCE, Head_circum$HEIGHT)
```
The correlation coefficiebt r for the linear model is 0.8708869

## Does r suggest a linear relationship that is weak, moderate, strong, or very strong?

The linear relationship is strong with a correlation coefficient of 0.8708869


## What is the value of the standard error for the explanatory variable?  Explain what it means in two or sentences.

```{r}
summary(removed_variable)
```

The standard error of the explanatory variable is 0.1655, this means that
0.1655 is the typical distance a sample height coefficient and the true population height coefficient.
