---
title: 'DATA 413: Classwork/Lab 6'
author: "Frankie Tyndall"
date: '2022-07-19'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(data.table)
flight3 <- fread("nycdata.csv")
flight4 <- read_csv("nycdata.csv")

```


## Dataset by data.table
```{r}
flight3

```

## Dataset by Tidyverse

You can also embed plots, for example:

```{r}
flight4
```
## Use and show data.table code to select the variables year, month, day, and hour from the imported flights data

```{r}
variables_ymd <- flight3[, .(year, month, day, hour)]
variables_ymd

```
## Use and show data. table code to produce a table that shows a carrier of DL, an origin of JFK and a destination of SEA

```{r}
carrier_fl <- flight3[origin == "JFK" & dest == "SEA" & carrier == "DL"]
carrier_fl

```

## Use and show data.table code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}

airtime_330 <- flight3[carrier == "UA" & month == 3 & air_time < 330]
airtime_330


```
##  Use and show tidyverse code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}
airtime_fl <- flight4 %>%
  filter(carrier == "UA", month == 3, air_time < 330)
airtime_fl
```
## Use the data.table method to add a variable called speed that is the average air speed of the plane in miles per hour. 

```{r}
flight3
sp <- flight3[, c("speed") := .(distance/(air_time/60))]
sp
```

## Use the tidyverse method to add a variable called speed that is the average air speed of the plane in miles per hour.

```{r}
perhour_tideverse <- flight4 %>%
  mutate(speed = (distance/(air_time/60)))
perhour_tideverse
```

## Show and use coding to change the carrier abbreviation of UA to UniitedAir

```{r}
# data.table method
flight3
ua <- flight3[carrier == "UA", carrier := "UniitedAir"]
ua[carrier == "UniitedAir"]
```

## Show and use coding to change the carrier abbreviation of UA to UniitedAir

```{r}

# tidyverse method 

changeUA <- flight4 %>%
  mutate(carrier = recode(carrier, "UA" = "UniitedAir")) %>%
  filter(carrier == "UniitedAir")
changeUA
```
